On Cybersecurity\\Science and Engineering\footnote{Confidential, restricted to the authors. Property of V-Research S.r.l.}

### 2020-03-24 abstract.tex
minor fix in abstract

The objective of this research is to develop of a theory that defines
(all and only) the possible insecurity and security configurations of
any abstract system. The theory is structured upon other theories that 
defines how a component of a system can be abstracted into an agent, defining how
agents can be formalized (both syntactically and semantically) to
describe an abstract system, such as a graph. Some of these theories
(e.g. used for the semantic
definition of the abstract system) are the epistemological definition
of knowledge, the Belief-Desire-Intent and the Assertion-Belief-Fact 
framework of reference, 
mereology, and topological structure. We argue that a mereology is the
most appropriate abstract underlying structure, do to its generality,
for defining the expressiveness of the system abstraction.  Furthermore, a
mereology allows us to define an ontology rather than a taxonomy.  We
also correlate different abstractions of the system to the TRL and the
engineering V-model.

>>>>

The objective of this research is to develop of a theory that defines
(all and only) the possible insecurity and security configurations of
any abstract system. The theory is structured upon other theories that 
defines how a component of a system can be abstracted into an agent, defining how
agents can be formalized (both syntactically and semantically) to
describe an abstract system, such as a graph. Some of these theories
(e.g. used for the semantic
definition of the abstract system) are the epistemological definition
of knowledge, the Belief-Desire-Intent and the Assertion-Belief-Fact 
framework of reference, 
mereology, and topological structure. We argue that a mereology is the
most appropriate abstract underlying structure, due to its generality,
for defining the expressiveness of the system abstraction.  Furthermore, a
mereology allows us to define an ontology rather than a taxonomy.  We
also correlate different abstractions of the system to the TRL and the
engineering V-model.
